Advice on describing Bayesian analysis of neutron and X-ray reflectometry

### 2022-07-14 src/tex/ms.tex
Section3 suggestions

Bayes theorem (given in Equation~\ref{equ:bayes}) consists of the product of the prior and the likelihood. 
The former describes our current understanding of the system before we conduct some experiments, while the latter describes the understanding that we gain from the data. 
Therefore, we must state how the likelihood for a given model and data is calculated, in particular, because although Equation~\ref{equ:likelihood} is a common approach, it assumes a normally distributed uncertainty. 
While a normally distributed uncertainty is the most common, it may not be accurate in all circumstances, for example, when low numbers of counts are present, a Poisson uncertainty may offer a more accurate description.

>>>>

Bayes theorem (given in Equation~\ref{equ:bayes}) consists of the product of the prior and the likelihood. 
The former describes our current understanding of the parameters before we conduct some experiments, while the latter describes how well the data is described by the model parameters. 
% ARJN we're not offering the reader suggestions on how to state this. Can they just state that they used packageX with version Y with likelihood option Z?
% ARJN there are multiple ways of weighting data, I'm not sure most users would know the details of how the likelihood is calculated in a given package.
% ARJN Should package authors state how this is done more comprehensively?
Therefore, we must state how the likelihood for a given model and data is calculated, in particular, because although Equation~\ref{equ:likelihood} is a common approach, it assumes a normally distributed uncertainty for a measured reflectivity value. 
% ARJN I think this is something like less than 30 (10?)???
While a normally distributed uncertainty is the most common, it may not be accurate in all circumstances, for example, when low numbers of counts are present, a Poisson uncertainty may offer a more accurate description.
